\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
 
% Supervisors
I would like to first acknowledge my supervisor Michael Norrish for all the guidance and support that he has given with HOL, for being my first port of call throughout this project, for helping to edit this text at its many stages, and for the pentagram (I hope I have done the idea justice). I would also like to thank my co-supervisor John Slaney for teaching me what there is to know about \textbf{R}, for pointing me in the right direction through the more obscure parts of the proofs seen in this thesis, and for passing on some of the aural history of Relevant Logic that are not found in any paper or book on the subject. 

% parents and sister
For every phone call, home visit, and for only being a few minutes away when I needed them; I would like to thank my parents Colin and Sandra, and my sister Amelia. 
Dad, thank you for being a support from which I was reflect clearly and calmly on my own thinking the past year and helping me get through the tough times. 
Mum, thank you for putting it all into perspective, telling me to go for a walk or a swim, and not spend my entire year attached to my computer. 
Amelia, thank you for being a voice of reason throughout this thesis and for telling me to get over myself when it mattered most.  

% editors
Thank you so much to Robynne Furini and Isabel Richards for volunteering to edit this tome as it neared its completion and for dealing with my many \emph{Taylorisms} along the way.   

% friends
Lastly I would like to thank Aditya Chilukuri, Seraina Elia, Robynne Furini, Craig Furini, Isabel Richards, and Nicholas Standen for everything they have done, each in their own way, to keep me human throughout the past year; this thesis would not have been written without you.   